MS_CNuptake.Rmd

### 2022-10-23 MS_CNuptake.Rmd
update

NPP_all$age_a <- log(NPP_all$mapped_age)
NPP_all$Tg_a <- NPP_all$Tg
NPP_all$PPFD_a <- log(NPP_all$PPFD)
NPP_all$vpd_a <- log(NPP_all$vpd)
NPP_all$fAPAR_a <- NPP_all$fAPAR
NPP_all$CNrt_a <- log(NPP_all$CNrt)
NPP_all$LMA_a <- log(NPP_all$LMA)
NPP_all$vcmax25_a <- log(NPP_all$vcmax25)
NPP_all$ndep_a <- log(NPP_all$ndep)

@@

### BP
```{r}
BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
#bp_model <- (lmer(tnpp_a~Tg_a+observedfAPAR_a+obs_age_a+PPFD_a+alpha_a+(1|site_a),data=BP_dataset))
#summary(bp_model)

>>>>

NPP_all$age_a <- log(NPP_all$mapped_age)
NPP_all$Tg_a <- NPP_all$Tg
NPP_all$PPFD_a <- log(NPP_all$PPFD)
NPP_all$PPFD_total_a <- log(NPP_all$PPFD_total)
NPP_all$vpd_a <- log(NPP_all$vpd)
NPP_all$fAPAR_a <- NPP_all$fAPAR
NPP_all$CNrt_a <- log(NPP_all$CNrt)
NPP_all$LMA_a <- log(NPP_all$LMA)
NPP_all$vcmax25_a <- log(NPP_all$vcmax25)
NPP_all$ndep_a <- log(NPP_all$ndep)

@@

### BP
```{r}
#ppfd_total check - BP using total_ppfd (D added but ppfd_total removed)
BP_dataset_ppfd_total <- na.omit(NPP_forest[,c("tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_total_a","vpd_a","site_a")])
stepwise(BP_dataset_ppfd_total,"tnpp_a")[[1]]
stepwise(BP_dataset_ppfd_total,"tnpp_a")[[3]]
bp_best <- (lmer(tnpp_a~Tg_a+fAPAR_a+age_a+CNrt_a+vpd_a+(1|site_a),data=BP_dataset_ppfd_total))
summary(bp_best)
bp_less_best <- (lmer(tnpp_a~Tg_a+fAPAR_a+age_a+CNrt_a+vpd_a+PPFD_total_a+(1|site_a),data=BP_dataset_ppfd_total))
summary(bp_less_best)

BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
#bp_model <- (lmer(tnpp_a~Tg_a+observedfAPAR_a+obs_age_a+PPFD_a+alpha_a+(1|site_a),data=BP_dataset))
#summary(bp_model)
